% !TeX root = ../dd.tex
In this section the requirements specified in the RASD are mapped to the components defined above. For brevity,
the API Gateway is omitted as, since it mediates most of the operations, it would need to be specified in almost
all requirements.
\begin{center}
    \begin{longtable}{|l|p{8cm}|p{5cm}|}
        \hline
              & \textbf{Description}                                                                                                                                                           & \textbf{Components}                                                        \\\hline
        \hline
        \endhead
        \hline
        \endfoot
        \hline
        \caption{Components traceability matrix}
        \label{table:Components traceability matrix}
        \endlastfoot
        R1    & The system shall allow users to log in with SSO.                                                                                                                               & \textbf{User Manager}                                                      \\\hline
        R2    & The system shall allow the student to provide information for their CVs.                                                                                                                    & \textbf{Platform Manager}                                                  \\\hline
        R2.1  &  The system shall allow the students to specify their personal information,
like name, contact and personal ambition.                                                                                      & \textbf{Platform Manager, User Manager}                                                  \\\hline
        R2.2  & The system shall allow the students to specify their education experience,
including their academic background.                                    & \textbf{Platform Manager}                                  
\\\hline
        R2.3  & The system shall allow the students to specify their past work experience,
specifying job title, company name, duration and technologies used.                                                                                                                    & \textbf{Platform Manager}                            \\\hline
        R2.4  & The system will allow students to specify their technical and soft skills.                                                                                                     & \textbf{Platform Manager}                    \\\hline
        R2.5  & The system shall allow the students to specify their project and research,
including the title, duration and description.                                                                                                     & \textbf{Platform Manager}                     \\\hline
        R2.6  & The system shall allow the students to specify their extracurricular activities, including the name, organization and achievements.                                                                                                     & \textbf{Platform Manager}                    
        \\\hline
        R2.7  & The system will allow students to specify their knowledge of languages,
including the level and any certifications.                                                                                                     & \textbf{Platform Manager}                 
\\\hline
        R2.8  & The system shall allow students to specify their availability.                                                                                                     & \textbf{Platform Manager}                   \\\hline
        R2.9  & The system will allow the students to add additional information.                                                                                                     & \textbf{Platform Manager}                                                        \\\hline
        R3    & The system shall allow the students to join an internship.                                       & \textbf{Platform Manager}                                             \\\hline
        R3.1    & The system shall help the students to create a customized CV for each company.                                                                                                                 &\textbf{Platform Manager}                                                  \\\hline
        R4    & The system shall allow the students to be notified when a new applicable internship becomes available.                                                                            & \textbf{Reccomendations Manager, Notification manager}                                                  \\\hline
        R5    & The system shall allow the company employee to create an internship.                                                                            & \textbf{Reccomendations Manager}                                                  \\\hline
        R5.1  & The system shall allow the company employee to specify the title of the
internship.                                                                                   & \textbf{Reccomendations Manager}                                                  \\\hline
        R5.2  &  The system shall allow the company employee to specify the description,
helped by an AI, of the internship.                                                                                                              & \textbf{Reccomendations Manager}                                                  \\\hline
        R5.3  & The system shall allow the company employee to specify the requirement of the internship.                                                                                                           & \textbf{Reccomendations Manager}                                                  \\\hline
        R5.4  & The system shall allow the company employee to specify the duration of the internship.                                                                                                             & \textbf{Reccomendations Manager}                          \\\hline
        R5.5  & The system shall allow the company employee to specify the availability of the internship.                                                                                                       & \textbf{Reccomendations Manager}                          \\\hline
        R5.6  & The system shall allow the company employee to specify other information about the internship.                                                                                                            & \textbf{Reccomendations Manager}                                                                                                 \\\hline
        R6    & The system shall allow the company employee to be notified when a new potentially interesting student becomes available.                                                                  & \textbf{Reccomendations Manager, Notification Manager}                                                  \\\hline
        R7    & The system shall allow the student to view a personalized homepage after inserting his CV’s information.                                                                                          & \textbf{Reccomendations Manager}                                              \\\hline
        R8    &  The system shall allow the company employee to view a personalized homepage after publishing an internship.                                                                                               & \textbf{Reccomendations Manager}                                                       \\\hline
        R9    & The system shall allow the company to write a complaint to the university.                                                                                              & \textbf{Relation Manager}
            \\\hline
        R10   & The system shall allow the students to write a complaint to the university.                                                       & \textbf{Relation Manager}                                                  \\\hline
        R11   & The system shall allow students to chat with his company.                            & \textbf{Platform Manager}                                                  \\\hline
        R12   & The system shall allow companies employee to chat with his trainee.                                                                 & \textbf{Platform Manager}                                                  \\\hline
        R13   & The system shall allow universities employee to chat with his students. & \textbf{Platform Manager}                                                  \\\hline
        R14   & The system shall allow the student to insert initial information.                                                                                                             & \textbf{Reccomendations Manager}                                                  \\\hline
        R15   & The system shall allow the student and the company to arrange a meeting.                                                                            & \textbf{Platform Manager, Notification Manager}                            \\\hline
        R16   & The system shall send a meeting link for the interview to the student and the company.               & \textbf{Platform Manager, Notification Manager}                                                  \\\hline
        R17   & The system shall allow the student to write on a logbook to inform the university on the status of his internship.                                                                                                                      & \textbf{Relation Manager}                                                                       \\\hline
    \end{longtable}
\end{center}
